dispRity manual

### 2017-05-30 doc/dispRity-manual.Rmd
disparity.per.group manual

This is a package for measuring disparity in `R`. It allows users to summarise ordinated matrices (e.g. MDS, PCA, PCO, PCoA) into single values so they can easily be compared.
<!-- Add version and table of content here! -->

@@

You can cite both the package or this manual with the following citation:
> Guillerme, T. (2016). dispRity: a package for measuring disparity in R. Zenodo. 10.5281/zenodo.55646

@@

One other typical analysis done with disparity is to look at the difference in disparity between several groups.

>>>>

This is a package for measuring disparity in `R`.
It allows users to summarise ordinated matrices (e.g. MDS, PCA, PCO, PCoA) into single values so they can easily be compared.
This manual is based on the version `1.0`.

@@

You can cite both the package or this manual with the following citation:

> Guillerme, T. (2016). dispRity: a package for measuring disparity in R. Zenodo. 10.5281/zenodo.55646

@@

Alternatively, you can be interested in looking at disparity between groups rather than through time.
For example, on question could be is there a difference in disparity between two groups?

To perform such analysis, you will need:

 * An ordinated matrix (always!)
 * A list of group members: this list should be a list of numeric vectors or names corresponding to the row names in the matrix. For example `list("a" = c(1,2), "b" = c(3,4))` will create a group _a_ containing elements 1 and 2 from the matrix and a group _b_ containing elements 3 and 4. Note that elements can be present in multiple groups at once.
 * Your definition of disparity (here the sum of variances)
